IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
nit
wip, pulling

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced(left).}
\end{figure}
%
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
(This task is part of the trusted computing base (TCB) and has access
to the full Node.js API.)
%
While V8 provides a means for sharing objects between contexts (used
by same-origin contexts in Blink), our system conservatively restricts
the kinds of messages that can be exchanged by tasks.
%
Concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
Our implementation, however, is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

@@

>>>>

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
(This task is part of the trusted computing base (TCB) and has access
to the full Node.js API.)
%
While V8 provides a means for sharing objects between contexts (used
by same-origin contexts in Blink), our system conservatively restricts
the kinds of messages that can be exchanged by tasks.
%
Concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
Our implementation, however, is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

While the described system implements |specLangJS seqf|, Node.js
applications may require access to the file system, HTTP server, HTTP
client, etc.

@@

\Red{TODO: note that if the target language allows inspecting if
  result is exception we can implement Breeze's NAV (vs. just
propagating)}
